A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/interaction.tex
fixed conflict, I prefer to say only figure B

@@

{\bf Initiate:} Users confirm their desire to connect to a device by tapping on the Glass touchpad. The next section on disambiguation deals with cases in which multiple devices received valid IR signals. At this point, all further communication switches over to the 802.15.4 wireless network so that line of sight to the target is no longer needed.

{\bf Control:} Glass displays a user interface for parameters of the chosen device. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters; single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters. This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.

>>>>

% \begin{figure}[t!]
% \centering
% \includegraphics[width=0.5\columnwidth]{figures/screenshot_LAMP_CONTROL.png}
% \caption{ }
% \label{fig:control_lamp}
% \end{figure}

% \begin{figure}[t!]
% \centering
% \includegraphics[width=0.5\columnwidth]{figures/screenshot_TV_CONTROLS.png}
% \caption{( devices. }
% \label{fig:control_tv}
% \end{figure}

\begin{figure}
\centering
\begin{subfigure}{.5\columnwidth}
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/screenshot_LAMP_CONTROL.png}
  \caption{Lamp control}
  \label{fig:control_lamp}
\end{subfigure}%
\begin{subfigure}{.5\columnwidth}
  \centering
  \includegraphics[width=0.9\columnwidth]{figures/screenshot_TV_CONTROLS.png}
  \caption{Video player control}
  \label{fig:control_tv}
\end{subfigure}
\caption{Screenshots of appliance controls}
\label{fig:test}
\end{figure}

@@

{\bf Initiate:} Users confirm their desire to connect to a device by tapping on the Glass touchpad (Figure~\ref{fig:interaction}C). The next section on disambiguation deals with cases in which multiple devices received valid IR signals. At this point, all further communication switches over to the 802.15.4 wireless network so that line of sight to the target is no longer needed.

{\bf Control:} Glass displays a user interface for parameters of the chosen device. The interface is controlled with the temple-mounted touchpad through the following gesture set: tapping toggles discrete parameters (such as power for a lamp as Figure~\ref{fig:control_lamp}); single finger swipe changes between available parameters; double finger swipe adjusts continuous parameters (such as volume for a video player as Figure~\ref{fig:control_tv}). This scheme was chosen because the touchpad is only comfortably operable in the coronal plane (front to back) but not in the saggital plane (up and down). 
Control commands are sent over XBee radios.
